\documentclass{resume}
\geometry{left=0.8cm,right=0.8cm,top=1cm,bottom=1cm,columnsep=1cm}
\usepackage{paracol}
\usepackage{setspace}
\usepackage{lipsum}
\usepackage{enumitem}

\renewcommand{\baselinestretch}{0.8}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }


\begin{document}

\fontfamily{ppl}\selectfont

\begin{huge}\noindent Simanga Hendry Khoza \end{huge}
\begin{paracol}{3}
        \noindent
        \clink{\href{mailto:h3khoza@gmail.com}{h3khoza@gmail.com}} \newline
        \clink{+27 81 249 0306}
\switchcolumn
\noindent
        \clink{ \href{www.h3ndry.me/about}{www.h3ndry.me/about}}\newline
        \clink{Pretoria, Gauteng, RSA}\newline
\switchcolumn
\noindent
        \clink{ \href{www.linkedin.com/in/h3ndry/}{linkedin.com/in/h3ndry}} \newline
        \clink{ \href{www.github.com/h3ndry}{github.com/h3ndry}}
\end{paracol}

    \csection{Skills}{\small
    \setlength{\parskip}{6pt}
        \noindent
        \clink {C\# | .NET | JavaScript | TypeScript | C++ | C | Bash  | Node | Python | SQL | NoSQL | Git } \newline \newline
        \clink {Linux | Gitlab | DevOps | CI/CD | Neovim | Jest | GitHub | Unit Testing | FastAPI | Docker } \newline
        \clink{  Microservices | Kubernetes | Frontend | Backend | Full-Stack | Tilt | BigQuery | Firebase } \newline
        }

    \csection{Experience}{\small
        \begin{itemize}
            \item \frcontent{Full-Stack Software Developer}{Kriterion - Pretoria, Melonpark}{July 2022 -- Present}
                \begin{itemize}[topsep=0pt,itemsep=0pt]
                {
                    \item Involved in initial phases of design analysis and elicitation of requirements.
                    \item Involved in deploying and hosting phases of .Net Core Web Application.
                    \item Deployed and maintain a .Net Core Web application on a Linux Server.
                    \item Managed MariaDB database.
                    \item Write a script to backup the MariaDB database daily.
                    \item Followed Test Driven Development to develop the Asp.Net Application.
                    \item Write clean, scalable code using C\# and .Net Framework.
                    \item Responsible for creating efficient design and developing User Interaction screens using HTML, CSS3, Bootstrap, JavaScript, and React/NextJS
                    \item Responsible for creating efficient design and developing User Interaction screens using HTML, CSS3, Bootstrap, JavaScript, and Angular
                    \item Used ADO.NET for SQL database interaction using Data Reader Dataset and Data view.

                    % \item Designed and Developed ASP.NET User Controls and used ASP.NET WebForms.
                    % \item Participated in the maintenance phase of the project
                    % \item Worked on GIT as version control. Utilized NPM scripts for building and testing environments in a Node.js application.
                    % \item Enhanced application performance by Angular 11 Component-based development.

                }
                \end{itemize}


            \item \frcontent{Junior Software Developer}{Copalcor (Pty) Ltd - Gemiston, Wideville}{January 2022 -- June 2022}
                \begin{itemize}[topsep=0pt,itemsep=0pt]
                {
                    \item Involved in initial phases of design analysis and elicitation of requirements.
                    \item Involved in deploying and hosting phases of .Net Core Web Application.
                    \item Deployed and maintain a .Net Core Web application on a Linux Server.
                    \item Managed MariaDB database.
                    \item Write a script to backup the MariaDB database daily.

                    % \item Followed Test Driven Development to develop the Asp.Net Application.
                    % \item Write clean, scalable code using C\# and .Net Framework.
                    % \item Responsible for creating efficient design and developing User Interaction screens using HTML, CSS3, Bootstrap, JavaScript, and React/NextJS
                    % \item Responsible for creating efficient design and developing User Interaction screens using HTML, CSS3, Bootstrap, JavaScript, and Angular
                    % \item Used ADO.NET for SQL database interaction using Data Reader Dataset and Data view.
                    % \item Designed and Developed ASP.NET User Controls and used ASP.NET WebForms.
                    % \item Participated in the maintenance phase of the project
                    % \item Worked on GIT as version control. Utilized NPM scripts for building and testing environments in a Node.js application.
                    % \item Enhanced application performance by Angular 11 Component-based development.

                }
                \end{itemize}

            \item \frcontent{.NET Developer Intern}{The Horizon HR - Mindrand}{March 2021 -- December 2022}
                \begin{itemize}[topsep=0pt,itemsep=0pt]
                {
                    \item Participated in the maintenance phase of a .NET Web API project
                    \item Developed Tests for Unit testing of the developed components using the N Unit Testing Framework
                    \item Involved in Application Support and releasing the fixes
                    \item Provide software support to end-users
                    \item Develop Front-End Applications using NextJS and React
                    \item Develop Front-End Applications using Angular and TypeScript

                    % \item Design and Develop an HTML form with a drag and drop feature in React.
                    % \item Design and Develop an HTML form with a drag and drop feature in Angular.
                    % \item Used SASS, SCSS, and CSS intensive to style Web Applications
                    % \item Addressed regular production bugs.
                    % \item Improved landing page and made it responsive to mobile devices.
                    % \item Involved in writing application level code to interact with APIs, Web services using AJAX, JSON, and XML

                }
                \end{itemize}


            \item \frcontent{C++ Programming Tutor }{Tshwane University of Technolog - Pretoria}{Febuary 2020 -- Dec 2020}
                \begin{itemize}[topsep=0pt,itemsep=0pt]
                {
                    \item Assisting students in understand the fundamentals of C++ and OOP in the context of C++
                    \item Assisting students with homework, projects, test preparation, papers, research, and other academic tasks
                }
                \end{itemize}

        \end{itemize}
    }

    \csection{Education}{\small
        \begin{itemize}
            \item \frcontent{N.Dip Computer Systems Engineering}{Tshwane University of Technology}{}{2020}
                \begin{itemize}[topsep=0pt,itemsep=0pt]
                {
                \item Achieve four distinctions in \textbf{Object-Oriented  Programming} and \textbf{Computer Skills}.
                    \item Modules: Communication Skills, Computer Skills, Digital Systems, Electrical Engineering, Electronics, Mathematics, Programming, Network Systems, Project, Digital Process Control, Operating Systems, Systems Analysis, Database Principles, Logic Design, Operational Research, Software Engineering
                }
                \end{itemize}


            \item \frcontent{High School Diploma}{Sincobile Secondary School}{}{2013}
                \begin{itemize}[topsep=0pt,itemsep=0pt]
                {
                    \item Achieve a distinction in \textbf{Mathematics} and levels 6 and 5 in the rest of the subjects
                }
                \end{itemize}

        \end{itemize}
    }


    \csection{Projects}{\small
        \begin{itemize}
            \item \fpcontent{Metal Purchasing System \clink{\href{https://45.79.173.203}{[45.79.173.203]}}}
                {A Full-Stack Web application built with \textbf{.Net Core 5}, The application simplifies the process of managing orders through a spreadsheet. It allows the user to create an order and send an email to the supplier. The application  is running on a Debian server using apache web sever}{}


            \item \fpcontent{Music Web Application\clink{\href{https://magibela.netlify.app/}{[magibela.netlify.app/]}}}
                {Music Web Application built with Javascript, HTML, and CSS that calls the Spotify REST API to play a top song of an artist}{}


            \item \fpcontent{Online Cellphone Store\clink{\href{https://cell-phone-store.netlify.app/}{[https://cell-phone-store.netlify.app/]}}}
                {React Single Page Application. A Demo Online Website that sells Cellphones. I have used Context Management to manage the state of the application}{}

        \end{itemize}
    }


    \csection{CERTIFICATIONS}{\small
        \begin{itemize}
            \item { Azure DevOps Engineer Exper - issued: 8 October 2021 - \clink{\href{https://www.credly.com/badges/80f2454f-f8de-4e74-9575-a01edf459fde}{[https://cutt.ly/DRI8NYP]}}}
            \item { Azure Developer Associate- issued: 8 July 2021 - \clink{\href{https://www.credly.com/badges/2b9449fa-ea3c-4baa-9362-2b1c6f69636e}{[https://cutt.ly/tRI4WYo]}}}
            \item { Azure Fundamentals - issued: 26 April 2021 - \clink{\href{https://www.credly.com/badges/eb7f2969-df90-4138-b898-bcb9f57389e1}{[https://cutt.ly/sRI3GgJ]}}}
        \end{itemize}
    }

% \end{paracol}
\end{document}
